### 2024-05-16 tex/aq_sankey.tex
Adjust sublimation label position
ML (mass loss) -> MG (mass gain)

    \sankeyset{ice}
    \sankeynode{ name=ML, quantity=\Q{FRET}+\Q{IL}, at={[xshift=8mm]SF.left}, anchor=right}
    \sankeystart[red]{ML}
    \sankeyadvance[red-to-ice]{ML}{1cm}
    \sankeyfork{ML}{\Q{FRET}/FRET, \Q{IL}/IL}
    \sankeydubins[minimum radius=2mm]{IL}{GROSS-from-IL}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{30}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{-30}
    \sankeyadvance{FRET}{3cm}
    \sankeydubins{FRET}{FRET-DYN}

@@

    \node[anchor=center, align=center, shift=({-0.2cm,-1cm})] at (SU-out.center) {Sublimation\\(\sankeygetnodeqty{SU-out})};

    \node[anchor=center, align=center, shift=({0cm,2.25cm})] at (ML.center) {Mass loss (\sankeygetnodeqty{ML}) = \\SMB \& Dynamics (\sankeygetnodeqty{IL})\\+ Frontal retreat (\sankeygetnodeqty{FRET})};

>>>>

    \sankeyset{ice}
    \sankeynode{ name=MG, quantity=\Q{FRET}+\Q{IL}, at={[xshift=8mm]SF.left}, anchor=right}
    \sankeystart[red]{MG}
    \sankeyadvance[red-to-ice]{MG}{1cm}
    \sankeyfork{MG}{\Q{FRET}/FRET, \Q{IL}/IL}
    \sankeydubins[minimum radius=2mm]{IL}{GROSS-from-IL}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{30}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{-30}
    \sankeyadvance{FRET}{3cm}
    \sankeydubins{FRET}{FRET-DYN}

@@

    \node[anchor=center, align=center, shift=({0.2cm,1cm})] at (SU-out.center) {Sublimation\\(\sankeygetnodeqty{SU-out})};

    \node[anchor=center, align=center, shift=({0cm,2.25cm})] at (MG.center) {Mass loss (\sankeygetnodeqty{MG}) = \\SMB \& Dynamics (\sankeygetnodeqty{IL})\\+ Frontal retreat (\sankeygetnodeqty{FRET})};
